---
title: "Final Project Markdown"
author: "Matthew Luu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# R Project: Air Quality Analysis

This project focuses on analyzing the built-in `airquality` dataset in R.

## Function: calculate_mean_temp

This function calculates the mean temperature.

### Inputs

- `data`: The `airquality` dataset.

### Outputs

- The mean temperature.

### Code

```{r}
calculate_mean_temp <- function(data) {
  mean(data$Temp, na.rm = TRUE)
}
```

## Function: calculate_max_ozone
This function calculates the maximum ozone value

### Inputs
- `data`: The `airquality` dataset

### Outputs
- The maximum ozone value

```{r}
calculate_max_ozone <- function(data) {
  max(data$Ozone, na.rm = TRUE)
}

```

### Insights and Challenges

During the development process, I learned that handling missing values is crucial in data analysis. One challenge was understanding the best method to handle these missing values without skewing the data.

#### Improvements

For future improvements, I plan to implement more functions to analyze other variables in the dataset.